Supplementary Materials

### 2018-12-12 Manuscript/sup_mat/sup_mat.Rmd
More sup_mat work
Added some new plots.
Started work on adding information about the ACS task and its analysis

## Adaptive Choice
For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance. Participants were give 10 practice trials (check this) before starting the actual experiment. (Check how many blocks as well). Participants were told they were to search for a target number (2-5 inclusive). There would be two of these target numbers on every trial; one in a blue square and one in a red square. They were told they only needed to report one of these numbers. The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively). Participants were instructed to be as fast and accuracte as possible. They were also told there would be a tone if they were to report a number that was not present within any of the boxes matching the two target colours.

## Foraging 
Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately. There were (get number of objects on display, I think it was 40?), half of which were the targets for that trial. The squares and circles subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).

Before starting the experiment, participants had 10 (check this number) practice trials to familiarise themeselves with the task. After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition. This took approximately 20 minutes.

@@

@@

## Adaptive Choice

>>>>

## Adaptive Choice
For this task, participants were sat approximately 47cm from the screen though no chin rest was used to ensure a constant viewing distance. Participants were give 10 practice trials before starting the actual experiment which consisted of 288 trials. Participants were told they were to search for a target number (2-5 inclusive). There would be two of these target numbers on every trial; one in a blue square and one in a red square. They were told they only needed to report one of these numbers. The squares subtended between ~1.1&deg; and ~1.3&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively). Participants were instructed to be as fast and accuracte as possible. They were also told there would be a tone if they were to report a number that was not present within any of the boxes matching the two target colours.

## Foraging 
Same as the in the Adaptive Choice task, participants were not sat in a chin rest and so viewing distance was approximately. There were 84 objects on screen, half of which were the targets for that trial. The squares and circles subtended between ~0.6&deg; and ~0.7&deg; depending on the screen resolution the participant was tested at (either 1600x1200 or 1400x1050, respectively).

Before starting the experiment, participants had 5 practice trials to familiarise themeselves with the task, after which they would begin the real task which cosisted of 20 trials. After completing the task with either the feature or conjunction search, participants would then repeat the task in the remaining condition. This took approximately 20 minutes.

@@

```{r processing ACS data, echo = FALSE}
# load data 
load("scratch/dat_ACS")

# filter out participants that were removed 
dat_ACS <- dat_ACS %>%
  filter(SubNo >= 5)

# probably want to work out things like accuracy etc?
# as in, exclude participants that are around chance level

```{r processing Foraging data, echo = FALSE}
# load data 
load("scratch/dat_for")

# filter out participants that were removed 
dat_for <- dat_for %>%
  filter(sub_no >= 5)

@@

## Adaptive Choice
```{r ACS plotting, echo = FALSE, message = FALSE, fig.align = "center"}
# what sort of things do we care about....

# RT by optimal choice
plt <- dat_ACS %>%
  na.omit() %>%
  mutate(Optimal_Choice = as.factor(Optimal_Choice)) %>%
  filter(Block_num > 0) %>%
  mutate(se = sd(RT)/sqrt(n())) %>%
  filter(RT > RT - 3*se,
         RT < RT + 3*se,
         RT > 300) %>%
  ggplot(aes(RT/1000, fill = Optimal_Choice)) + 
  geom_histogram() +
  theme_bw() + 
  theme(strip.text.x =  element_blank()) + 
  coord_cartesian(expand = FALSE) + 
  scale_fill_ptol() +
  facet_wrap(~ Optimal_Choice) 
plt$labels$x <- "Response Time (secs)"
plt$labels$fill <- "Optimal Choice"
plt

# what about RT by number of optimal choices
# only: - correct trials
#       - RT > 300ms
plt2 <- dat_ACS %>%
  na.omit() %>%
  filter(Block_num > 0) %>%
  mutate(se = sd(RT)/sqrt(n())) %>%
  filter(RT > RT - 3*se,
         RT < RT + 3*se,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_RT = mean(RT),
            sum_optchoices = sum(Optimal_Choice)) %>%
  ggplot(aes(sum_optchoices, mean_RT, label = SubNo)) + 
  geom_point() + 
  geom_text() + 
  theme_bw()
plt2

# Get accuracy for each participant 
# probably want to exclude participant 39 going by their accuracy 
plt3 <- dat_ACS %>%
  filter(Block_num > 0) %>%
  mutate(se = sd(RT)/sqrt(n())) %>%
  filter(RT > RT - 3*se,
         RT < RT + 3*se,
         RT > 300) %>%
  group_by(SubNo) %>%
  summarise(mean_acc = mean(Acc)) %>%
  mutate(mean_acc_ov = mean(mean_acc)) %>%
  ggplot(aes(SubNo, mean_acc)) + 
  geom_point() + 
  theme_bw()
plt3
